Modeling Interventions

### 2021-08-13 model_interventions.Rmd
added refs, cleaned up model code a bit
looking at book vs. CHILDES vs. SUBTLEX frequencies for CDI/non-CDI words

```{r, summary-tables, echo=F}
# Gilkerson et al. 2017 Table 2: standardized AWC

@@

>>>>

```{r, summary-tables, echo=F}
# Table 1 O’Reilly, d’Apice, von Stumm
# Adult word count N=107 Mean=54065.00 SD=17135.33 Min=15038.02 Max=99684.85 Skew=0.37 Kurtosis=0.05

# Gilkerson et al. 2017 Table 2: standardized AWC

@@

# log-normal distribution?
require(fitdistrplus)
mc_tok = df$mother_child_tokens_hr[!is.na(df$mother_child_tokens_hr)]
ac_tok = df$adult_child_tokens_hr[!is.na(df$adult_child_tokens_hr)]
all_tok = df$all_tokens_hr[!is.na(df$all_tokens_hr)]
plotdist(mc_tok, histo=T, demp=T) # 113
plotdist(ac_tok, histo=T, demp=T) # 42
plotdist(all_tok, histo=T, demp=T) # 83

# based on skew vs. kurtosis, look like beta distributions
descdist(df$mother_child_tokens_hr[!is.na(df$mother_child_tokens_hr)], boot=1000)
descdist(df$adult_child_tokens_hr[!is.na(df$adult_child_tokens_hr)], boot=1000)
descdist(df$all_tokens_hr[!is.na(df$all_tokens_hr)], boot=1000)

fb <- fitdist(mc_tok/max(mc_tok+1e-9), method="mme", "beta") # beta: vals must be in [0-1], so I scaled...
# llik = -7.76

summary(fitdist(mc_tok/max(mc_tok+1e-9), "weibull")) # llik: 23.4 ?

fw <- fitdist(mc_tok, "weibull") # llik: -902
fg <- fitdist(mc_tok, "gamma", method="mme") # llik: -902 fails with method="mle" error code 100
fln <- fitdist(mc_tok, "lnorm") # llik: -907.9991
fn <- fitdist(mc_tok, "norm") # llik: -920.7385
plot.legend <- c("Weibull","log-normal", "gamma")
par(mfrow=c(2,2))
denscomp(list(fw, fln, fg), legendtext=plot.legend)
qqcomp(list(fw, fln, fg), legendtext=plot.legend)
cdfcomp(list(fw, fln, fg), legendtext=plot.legend)
ppcomp(list(fw, fln, fg), legendtext=plot.legend)
